COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-04-27 main.tex
Start looking at effect of pericenter precession near resonances

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/ae.png}
    \caption{The semimajor axis - eccentricity state of the remaining planetesimals are shown at the end of the CJ (top) and EJ (bottom) 
    simulations. The vertical bars mark the nominal locations of prominent resonances. Planetesimals affected by resonance with Jupiter gain
     eccentricity, and due to conservation of the Jacobi energy, reduce their semimajor axes. This produces the curved fingerlike structure 
     extending off of the resonances. In the EJ case, some bodies in resonance take on eccentricities smaller than their initial forced values as 
     they undergo libration.\label{fig:ae}}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/long_ph.png}
    \caption{The semimajor axis and pericenter orientation of remaining planetesimals at the end of the EJ simulation. All bodies start with their 
    pericenters closely aligned with Jupiter's ($\varpi = \pi$). Near the resonances, bodies undergo strong precession which randomizes their 
    orbital orientations. Two-body interactions between the planetesimals in resonance and nearby non-resonant planetesimals drags their 
    longitude of perihelia along with.\label{fig:long_ph}}
    \end{center}
\end{figure}

@@

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/coll_hist_r_inout_res.png}
    \caption{KDE of the number of collisions at a given heliocentric distance for planetesimals inside (left) and outside (right) of the 2:1 MMR. In the $e_{pl} = 2 e_{jup}$ case, a bump, rather than a dip appears near the 2:1 MMR (see figure \ref{fig:coll_hist_e_and_m}). This bump is produced by non-resonant planetesimals undergoing collisions near the center of the 2:1 MMR.\label{fig:coll_hist_r_inout_res}}
    \end{center}
\end{figure*}

>>>>

Also mention \citet{2020A&A...635A..10S}, looked at dust trapping in resonances with terrestrial SS planets. Also mention 
\citet{2020arXiv200408736G}, detection of a planetesimal collision around Fomalhut.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/ae.png}
    \caption{The semimajor axis and eccentricities of planetesimals at the end of the eccentric Jupiter simulations. Near the location of mean motion resonances, the resonant angle librates and drives corresponding oscillations in eccentricity. Due to the conservation of the Jacobi energy, these changes in eccentricity also drive slight, inward changes in semimajor axis.\label{fig:ae}}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=\columnwidth]{figures/long_ph.png}
    \caption{The semimajor axis and pericenter orientation of remaining planetesimals at the end of the eccentric Jupiter simulations. When the forced eccentricity of the planetesimal disk is large, planetesimals near the edge of the mean motion resonances become more resistant to precession induced by the resonances.\label{fig:long_ph}}
    \end{center}
\end{figure}

@@

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/coll_hist_r_inout_res.png}
    \caption{KDE of the number of collisions at a given heliocentric distance for planetesimals inside (left) and outside (right) of the 2:1 MMR. In the $e_{pl} = 2 e_{jup}$ case, a bump, rather than a dip appears near the 2:1 MMR (see figure \ref{fig:coll_hist_e_and_m}). This bump is produced by non-resonant planetesimals undergoing collisions near the center of the 2:1 MMR. In the right panel, the dashed curves represent collisions where the longitude of perihelion of either collider was strongly misaligned with Jupiter. In the high eccentricity case, bodies near the edge of the resonance with randomly oriented orbits can reach across the resonance and collide with planetesimals on the other side.\label{fig:coll_hist_r_inout_res}}
    \end{center}
\end{figure*}
